### 2019-10-29 thesis/txt/5-study.tex
renamings in big study data analysis

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
	\label{fig:categories-dataset}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
		\caption{Distribution of the Count of Categories within the Examples used for Configuartion in our Study}
		\label{fig:categorycount-examplecount-dataset}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{caption}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Category Distribution in Data Set}
Categories distributed in over data set
- why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
- Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
- Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.

\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{Successful Extractions per Number of Examples for PBE}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
		\caption{Successful Extractions per Number of Examples for TS}
		\label{fig:success-examples-ir}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-kw}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
		\caption{Successful Extractions per Number of Examples for RLR}
		\label{fig:success-examples-rn}
	\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
		\caption{Successful Extractions per Number of Examples for PBE}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-pbe.pdf}
		\caption{Precision of Extractions per Number of Examples for PBE}
		\label{fig:precision-pbe}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-pbe.pdf}
		\caption{Precision of PBE Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Reasons for PBE Runs to Fail}
		\label{fig:failure-reason-pbe}
	\end{minipage}
\end{figure}

@@

% Figure \ref{fig:success-all} shows how successful the four different tecnhiques were in our study.
% Figure \ref{fig:success-examples-pbe} shows that the success rate for PBE decreases with increasing example count for pbe. Section \ref{TODO ref to pbe section} explains in more detail whi this fails
% Figure \ref{fig:success-examples-ir} shows that the success rate for TS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-kw} shows that the success rate for KWS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-pbe} shows that

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
		\caption{Successful Extractions per Number of Examples for TS}
		\label{fig:success-examples-ir}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-ir.pdf}
		\caption{Precision of Extractions per Number of Examples for TS}
		\label{fig:precision-ir}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-ir.pdf}
		\caption{Precision of TS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-ir}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-kw}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-kw.pdf}
		\caption{Precision of Extractions per Number of Examples for SKWS}
		\label{fig:precision-kw}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-kw.pdf}
		\caption{Precision of SKWS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-kw}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
		\caption{Successful Extractions per Number of Examples for RLR}
		\label{fig:success-examples-rn}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-rn.pdf}
		\caption{Precision of Extractions per Number of Examples for RLR}
		\label{fig:precision-rn}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-rn.pdf}
		\caption{Precision of RLR Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-rn}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
	\label{fig:categories-dataset}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
		\label{fig:categorycount-examplecount-dataset}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{caption}
		\label{fig:xxxy}
	\end{minipage}
\end{figure}

\subsection{Category Distribution in Data Set}
Categories distributed in over data set
- why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
- Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
- Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
		\caption{Successful Extractions per Number of Examples for PBE}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
		\caption{Precision of Extractions per Number of Examples for PBE}
		\label{fig:precision-pbe}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
		\caption{Precision of PBE Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Reasons for PBE Runs to Fail}
		\label{fig:failure-reason-pbe}
	\end{minipage}
\end{figure}

@@

% Figure \ref{fig:success-all} shows how successful the four different tecnhiques were in our study.
% Figure \ref{fig:success-examples-pbe} shows that the success rate for PBE decreases with increasing example count for pbe. Section \ref{TODO ref to pbe section} explains in more detail whi this fails
% Figure \ref{fig:success-examples-ts} shows that the success rate for TS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-skws} shows that the success rate for KWS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-pbe} shows that

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
		\caption{Successful Extractions per Number of Examples for TS}
		\label{fig:success-examples-ts}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
		\caption{Precision of Extractions per Number of Examples for TS}
		\label{fig:precision-ts}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
		\caption{Precision of TS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-ts}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWSpdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWSpdf}
		\caption{Precision of Extractions per Number of Examples for SKWS}
		\label{fig:precision-skws}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWSpdf}
		\caption{Precision of SKWS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-RLR.pdf}
		\caption{Successful Extractions per Number of Examples for RLR}
		\label{fig:success-examples-rlr}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-RLR.pdf}
		\caption{Precision of Extractions per Number of Examples for RLR}
		\label{fig:precision-rlr}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-RLR.pdf}
		\caption{Precision of RLR Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-rlr}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
